INTELLIGENT SYSTEMS

### 2021-04-14 papers/paper_7.tex
finish 7.3.2

\subsubsection{Weighted K-SVD Model}
The following work is based on the method proposed in \cite{0884882814}. After obtaining 
the value of the mixed-noise \emph{Probability Density Function} (PDF), and 
assuming that the noise has a uniform distribution, we can derive the \emph{negative 
log-likelihood} function (\ref{PDF}) useful as {\bfseries{fidelity term}} in the variational 
method. 
\begin{equation}\label{PDF}
    L(u,\Theta) = - \sum_{x\in\Omega}\ln\sum_{k=1}^Kr_kp_k(u(x)-f(x))
\end{equation}
In order for this probability to be extended to more types of noise 
distribution, it is necessary to perform an optimization that minimizes the 
upper limit of the function (\ref{H function}). 
\begin{eqnarray}\label{H function}
    \mathcal{H}(u,\Theta,w) & = & - \sum_{x\in\Omega}\sum_{k=1}\ln\left[r_kp_k(u(x)-f(x))\right]w_k \nonumber \\
                  &   & + \sum_{x\in\Omega}\sum_{k=1}w_k(x)\ln{w_k(x)}  
\end{eqnarray}
To minimize $\mathcal{H}$, a minimization of $ w $ must be performed, which is a probability 
indicates the noise at each pixel, and an iterative minimization of the other 
two variables $ u $ and $ \Theta $.

@@

\subsubsection{Gaussian Mixture Model}
A Gaussian mixture model is a probabilistic model that assumes all the data 
points are generated from a mixture og finite number of Gaussian distributions 
with unknown parameters. The distributions of Gaussian noises change 
according to the assumed variance ($\sigma^2$) value. The new function $ \mathcal{H} $ will be 
as follows:
\begin{eqnarray}
    \mathcal{H}(u,r,\sigma^2,w) & = & \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^K\frac{(u(x)-f(x))^2}{\sigma^2_k}w_k(x)-\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{r_k}\nonumber \\
                                &   & + \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{\sigma^2_k}+\frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{w_k}(x)
\end{eqnarray}
The optimizations (\ref{uMin}) (\ref{ThetaMin}) (\ref{wMin}) of the parameters of (\ref{HFunction}) are adapted by 
including the two new parameters $r$ and $\sigma^2$, parameters that are included in 
$\Theta$.

>>>>

\subsubsection{Weighted K-SVD Model}
The following work is based on the method proposed in \cite{0884882814}. After obtaining 
the value of the mixed-noise \emph{Probability Density Function} (PDF), and 
assuming that the noise has a uniform distribution, we can derive the \emph{negative 
log-likelihood} function (\ref{PDF}) useful as {\bfseries{fidelity term}} in the variational 
method. 
\begin{equation}\label{PDF}
    \mathcal{L}(u,\Theta) = - \sum_{x\in\Omega}\ln\sum_{k=1}^Kr_kp_k(u(x)-f(x))
\end{equation}
In order for this probability to be extended to more types of noise 
distribution, it is necessary to perform an optimization that minimizes the 
upper limit of the function (\ref{H function}). 
\begin{eqnarray}\label{H function}
    \mathcal{H}(u,\Theta,w) & = & - \sum_{x\in\Omega}\sum_{k=1}\ln\left[r_kp_k(u(x)-f(x))\right]w_k \nonumber \\
                  &   & + \sum_{x\in\Omega}\sum_{k=1}w_k(x)\ln{w_k(x)}  
\end{eqnarray}
To minimize $\mathcal{H}$, a minimization of $ w $ must be performed, which is a probability 
indicates the noise at each pixel, and an iterative minimization of the other 
two variables $ u $ and $ \Theta $.

@@

\subsubsection{Gaussian Mixture Model}
A Gaussian mixture model is a probabilistic model that assumes all the data 
points are generated from a mixture og finite number of Gaussian distributions 
with unknown parameters. The distributions of Gaussian noises change 
according to the assumed variance ($\sigma^2$) value. The new function $ \mathcal{H} $ will be 
as follows:
\begin{eqnarray}\label{HFunctionGMM}
    \mathcal{H}(u,r,\sigma^2,w) & = & \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^K\frac{(u(x)-f(x))^2}{\sigma^2_k}w_k(x)-\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{r_k}\nonumber \\
                                &   & + \frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{\sigma^2_k}+\frac{1}{2}\sum_{x\in\Omega}\sum_{k=1}^Kw_k(x)\ln{w_k}(x)
\end{eqnarray}
The optimizations (\ref{uMin}) (\ref{ThetaMin}) (\ref{wMin}) of the parameters of (\ref{HFunctionGMM}) are adapted by 
including the two new parameters $r$ and $\sigma^2$, enclosed in $\Theta$, which will be minimized 
in turn. Through the optimization of these parameters it is possible to remove 
the mixed-noise Gaussian. In summary, all the steps carried out are 
illustrated in figure \ref{fig:EM-CNN}.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.7 \linewidth]{images/paper7/flowchart.png}
    \centering
    \caption{The flowchart of EM-CNN algorithm.}
    \label{fig:EM-CNN}
\end{figure}
Image degradation occurs using the additive noise model: 
$$ f = u + n $$
where $f$ is the observed image (the one resulting from the combination of 
noises), $u$ is the true image and $n$ is the introduced noise. The image $f$ will 
be the input of the CNN network which, through its denoise \cite{0884882819}, will perform 
a smoothing on the image obtaining a new image $u^{v+1}$. CNN applies two 
operations on this image in parallel. The first is that of the noise put back 
in which the noise present in the image f is extracted by simply subtracting 
the image $u^{v+1}$. Subsequently, to calcutale the fidelity term, the EM algorithm 
\cite{0884882814} is applied to this noise which has the task of estimating the error 
and classifying it by minimizing the terms of \ref{HFunctionGMM}. The minimization of each 
weight $w$ leads to a continuous updating of this parameter which translates 
into greater precision in determining the noise on each individual pixel. The 
estimation of the parameters allows to carry out the synthesis process, or to 
select a new fidelity term, for each pixel, based on the estimates made on the 
noise. The second operation is to apply the \emph{Total Variation Regularization} 
(TV) \cite{0884882802} on the starting image $u^{v+1}$ useful for carrying out a good 
restructuring of the image from noise and blurred data. The image $V^v$ with the 
updated w weights, will be the new input of the CNN network that through 
multiple iterative processes will improve until its convergence, or until the 
fidelity term will no longer change. The output returned by the model will 
consist of a restructured image ($u^*$) accompanied by the estimates of the 
individual noises ($n_1^ *, n_2^*$) applied at the beginning.
